---
title: "Vincent_Jin_Mini_Assignment1"
author: "Vincent Jin"
date: "2023-03-31"
output: pdf_document
---

# Mini Assignment 1
## Vincent Jin

# ============================================================ 
# 	Mini-assignment # 1
# ============================================================ 
# *** for each of the following questions, type “done” if you achieved it ***

# install R on your PC/Mac

## Done

# install RStudio on your PC/Mac

## Done

# install the following package: data.table

``` {r}
# install.packages("data.table")
```

## Done

# call the data.table library

``` {r}
library(data.table)
```

# install the following package: benchmarkme (it may take some time as it will install other packages)

``` {r}
# install.packages("benchmarkme")
```

## Done

# *** if you get an error, simply report the error (specially for Mac users) ***

## No error encountered

# call the benchmarkme library

``` {r}
library(benchmarkme)
```

# *** for each of the following questions, type the results after the question ***
# run "version" command in the console and provide the result

``` {r}
version
```

# run "memory.limit()" command in the console and provide the result

``` {r}
memory.limit()
```

# run "get_cpu()" command in the console and provide the result

``` {r}
get_cpu()
```

# run "data(sample_results)" command (no results will be shown in the console)

``` {r}
data("sample_results")
```

# run "plot(sample_results, blas_optimize = NULL)" command -- provide the ranks provided by R (usually 3 numbers printed in the console; you can ignore the plots!)

``` {r}
plot(sample_results, blas_optimize = NULL)
```

